Efficient pedigree recording for fast population genetics simulation

### 2018-01-11 forwards_paper.tex
Reposition msprime api section to just after 'working with tables'

@@

%%%%%%
\subsection*{Overview of \msprime\ APIs that enable the method}

\paragraph{Flexibility.}
To demonstrate the flexibility provided by the Tables API and provide an
implementation that decouples forward simulation internals from transfer of data
to \msprime\, we implemented a version of the simulations described in
``Simulation benchmarks'' separately in Python (see Appendix~\ref{ss:simupop}).
For this proof-of-concept implementation, the simulation engine invokes
callbacks at critical points of the simulation, and we infer nodes and edges
from the information that is provided. Rows are appended to the tables
one-by-one, and the tables are periodically sorted and simplified to control
memory usage.
It uses the \simupop{} library, interfacing with Python code (via our
package \ftprime{}) to simulate a discrete but large number of sites instead of the
infinite sites model; we provide results from this implementation alongside the
results from the \cpp\ implementation for simulations without selection  (see
Appendix~\ref{ss:timing_nosel}).
% $\mu$ and $r$ define per-base-pair mutation rate a
% the simulated sequence, in base pairs, as $L = \tfrac{\rho}{4N \mu}$.  We
% varied $N \in (1000, 10000)$, $\rho \in (10^3, 10^4)$.

>>>>

%%%%%%
\subsection*{The \msprime\ Tables API}

\paragraph{Flexibility.}
To demonstrate the flexibility provided by the Tables API and provide an
implementation that decouples forward simulation internals from transfer of data
to \msprime\, we implemented a version of the simulations described in
``Simulation benchmarks'' separately in Python (see Appendix~\ref{ss:simupop}).
For this proof-of-concept implementation, the simulation engine invokes
callbacks at critical points of the simulation, and we infer nodes and edges
from the information that is provided. Rows are appended to the tables
one-by-one, and the tables are periodically sorted and simplified to control
memory usage.
It uses the \simupop{} library, interfacing with Python code to simulate a
discrete but large number of sites instead of the infinite sites model; we
provide results from this implementation alongside the results from the \cpp\
implementation for simulations without selection  (see
Appendix~\ref{ss:timing_nosel}).
% $\mu$ and $r$ define per-base-pair mutation rate a
% the simulated sequence, in base pairs, as $L = \tfrac{\rho}{4N \mu}$.  We
% varied $N \in (1000, 10000)$, $\rho \in (10^3, 10^4)$.

@@
